TimeVaryingDetection_mrmr

### 2024-11-16 code/R/54188_ClassicCustomComparison_mrmr.Rmd
remove custom fit model function code

# Test my custom stan model with MLRG's public data from site 54188

    The modified stan model...

@@

**Load packages**
```{r}
library(cmdstanr)
library(mrmr)
library(ggplot2)
library(ggpubr)
```

## Modify mrmr::fit_model()

-   fit_model_custom() is a copy of mrmr::fit_model(), changed only to call on a modified version of the underlying stan model.

# Custom fit function using the updated Stan model file
fit_model_custom <- function(
  data,
  seed = NULL,
  refresh = NULL,
  init = NULL,
  save_latent_dynamics = FALSE,
  output_dir = NULL,
  output_basename = NULL,
  sig_figs = NULL,
  chains = 4,
  parallel_chains = getOption("mc.cores", 1),
  chain_ids = seq_len(chains),
  threads_per_chain = NULL,
  opencl_ids = NULL,
  iter_warmup = 1000,
  iter_sampling = 1000,
  save_warmup = FALSE,
  thin = NULL,
  max_treedepth = NULL,
  adapt_engaged = TRUE,
  adapt_delta = NULL,
  step_size = NULL,
  metric = NULL,
  metric_file = NULL,
  inv_metric = NULL,
  init_buffer = NULL,
  term_buffer = NULL,
  window = NULL,
  fixed_param = FALSE,
  show_messages = TRUE,
  compile = TRUE,
  ...
) {
  # updated to use my custom stan model
  stan_file <- "/Users/johnimperato/Desktop/Mossy-Pond/code/stan/JI_custom_twostate.stan" # specify local path

  model <- cmdstan_model(stan_file, ...)

  m_fit <- model$sample(
    data = data$stan_d,
    seed = seed,
    refresh = refresh,
    init = init,
    save_latent_dynamics = save_latent_dynamics,
    output_dir = output_dir,
    output_basename = output_basename,
    sig_figs = sig_figs,
    chains = chains,
    parallel_chains = parallel_chains,
    chain_ids = chain_ids,
    threads_per_chain = threads_per_chain,
    opencl_ids = opencl_ids,
    iter_warmup = iter_warmup,
    iter_sampling = iter_sampling,
    save_warmup = save_warmup,
    thin = thin,
    max_treedepth = max_treedepth,
    adapt_engaged = adapt_engaged,
    adapt_delta = adapt_delta,
    step_size = step_size,
    metric = metric,
    metric_file = metric_file,
    inv_metric = inv_metric,
    init_buffer = init_buffer,
    term_buffer = term_buffer,
    window = window,
    fixed_param = fixed_param,
    show_messages = show_messages
  )

  # Load all the data and return the whole unserialized fit object
  m_fit$draws() # Do not specify variables or inc_warmup.
  try(m_fit$sampler_diagnostics(), silent = TRUE)
  try(m_fit$init(), silent = TRUE)
  try(m_fit$profiles(), silent = TRUE)

  list(m_fit = m_fit, data = data)
}

@@

abund_recruit_comparison_plot <- ggarrange(classic_annotated, custom_annotated, ncol=2)

>>>>

# Model Comparison

**Classic mrmr model vs. modified mrmr model**

    The modified model...

@@

**Load packages**
```{r}
library(cmdstanr)
library(mrmr)
library(ggpubr)
```

@@

abund_recruit_comparison_plot_54188 <- ggarrange(classic_annotated, custom_annotated, ncol=2)
